The \project{unRAVE} catalog of X.X million detailed stellar abundances for chemodynamic studies

### 2016-08-16 article/unrave.tex
Add conditions

The exposure times (and resultant S/N ratios) for \rave\ were optimised to obtain
radial velocities for as many stars as possible.  Detailed chemical abundances were
always an important science goal of the survey, but this was a secondary objective.  
For this reason the distribution of S/N ratios of \rave\ spectra is considerably 
lower than other stellar spectroscopic surveys where chemical abundances are the 
primary motivation.  The \rave\ spectra have an effective resolution 
$\mathcal{R} \approx 7500$ and the distribution of S/N ratios peaks at 
$\approx$50~per~pixel$^{-1}$.  For comparison, the \project{GALAH} survey 
\citep{DeSilva_2015} --- which was specifically constructed for detailed chemical 
abundance analyses --- includes a wavelength range about 2.5 times larger at 
resolution $\mathcal{R} \approx 28,000$, and yet the \project{GALAH} project still 
targets for S/N $\gtrsim100$.

@@

Given the high-quality of the normalization performed by the \rave\ team, we chose
not to re-normalize the spectra.  Our tests demonstrated that the procedure 
outlined in \citet{Kunder_2016} is sufficient for our analysis procedure. Therefore,
there is a limited number of pre-processing steps that we conducted before our
analysis could begin.  Firstly, we calculated inverse variance arrays from the
fractional uncertainties provided, then re-sampled the flux and inverse variance
arrays onto a common rest-wavelength map for all stars.  Depending on the fibre 
used and the stellar radial velocity, the range of rest-frame wavelength values
varied for each star.  Given that fluxes were unavailable in the edge pixels for 
most stars, we excluded pixels outside of the rest wavelength range 
$8423.2\,{\rm \AA} \le \lambda \le 8777.6\,{\rm \AA}$.

@@

>>>>

The exposure times for \rave\ observations were optimised to obtain radial 
velocities for as many stars as possible.  Detailed chemical abundances were
always an important science goal of the survey, but this was a secondary objective.  
For this reason the distribution of S/N ratios in \rave\ spectra is considerably 
lower than other stellar spectroscopic surveys where chemical abundances are the 
primary motivation.  The \rave\ spectra have an effective resolution 
$\mathcal{R} \approx 7500$ and the distribution of S/N ratios peaks at 
$\approx$50~per~pixel$^{-1}$.  For comparison, the \project{GALAH} survey 
\citep{DeSilva_2015} --- which was specifically constructed for detailed chemical 
abundance analyses --- includes a wavelength range about 2.5 times larger at 
resolution $\mathcal{R} \approx 28,000$, and yet the \project{GALAH} project still 
targets for S/N $\gtrsim100$.

@@

Given the high-quality of the normalization performed by the \rave\ team, we chose
not to re-normalize the spectra.  Our tests demonstrated that the procedure 
outlined in \citet{Kunder_2016} is sufficient for our analysis procedure. Therefore,
there is a limited number of pre-processing steps that we conducted before our
analysis could begin.  Firstly, we calculated inverse variance arrays from the
fractional uncertainties provided, then re-sampled the flux and inverse variance
arrays onto a common rest-wavelength map for all stars.  Depending on the fibre 
used and the stellar radial velocity, the range of rest-frame wavelength values
varied for each star.  Given that fluxes were unavailable in the edge pixels for 
most stars, we excluded pixels outside of the rest wavelength range 
$8423.2\,{\rm \AA} \le \lambda \le 8777.6\,{\rm \AA}$.  This corresponds to about
30~pixels excluded on either side of the common wavelength array.

@@

\subsection*{Access the results electronically}

% TODO: Replace ZENODO-URL with a data url
Source code for this project is available at \texttt{\url{https://www.github.com/AnnieJumpCannon/RAVE}}.  This document was compiled from revision hash \githash\
in that repository.
Inferred labels and covariance matrices are available with associated metadata electronically at \texttt{\url{ZENODO-URL}}.  Please note that it is a condition of using these results that the fifth \rave\ data release by \citet{Kunder_2016} must (also) be cited, as the work presented here would not have been possible without the tireless efforts of the entire \rave\ collaboration, past and present.
